\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-16 NAR_DRAFT.tex
little fixes

\subsection{Convergence of the site-specific prior to the data generating distribution}
The context-dependent prior probability of mutation, the heart of \batcave, depends on the prior converging to a good representation of the data generating distribution within the set of high-confidence mutations.
We use the Kullback-Leibler (KL) divergence as a measure of the distance (or entropy difference) between the estimated prior and the actual simulated data generating distribution.
In Figure~\ref{NAR-kl_fig} we order mutations by descending MuTect probability value, and compute the KL divergence between the prior after adding each mutation and the data generating distribution.
For both whole exome and whole genome the prior converges to the data generating distribution easily within the number of available high-confidence mutations, which for the \citet{Griffith2015} leukemia is over 17000, and for our simulated data sets ranges between 1500 and 5000.

>>>>

\subsection{Convergence of the site-specific prior to the data generating distribution}
The context-dependent prior probability of mutation, the heart of \batcave, depends on the prior converging to a good representation of the data generating distribution within the set of high-confidence mutations.
We use the Kullback-Leibler (KL) divergence as a measure of the distance (or entropy difference) between the estimated prior and the actual simulated data generating distribution.
In Figure~\ref{NAR-kl_fig} we order mutations by descending MuTect probability value, and compute the KL divergence between the prior after adding each mutation and the data generating distribution.
For both whole exome and whole genome the prior converges to the data generating distribution easily within the number of available high-confidence mutations, which for the leukemia~\citep{Griffith2015} is over 17000, and for our simulated data sets ranges between 1500 and 5000.
